Rotations and Insecticide Resistance initial plots

### 2017-10-09 inst/documents/rotations_notes.Rmd
added more params to UI, and output of code

# TODO
~ test fitness_single_locus() from run_rot() and add to Rmd

>>>>

*9/10/17*
~ started first shiny UI : rotresist1
~ add rot interval and generations to rotresist

# TODO

~ seems that resistance evolves more slowly in later insecticides despite same params. Why ?

e.g. :
run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.01 , rotation_interval = 50 , eff = 0.7 , dom = 0.5 , rr = 0.5 , expo_hi = 0.7 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0.1 )

*Ian said first question is to assess whether there is any benefit to rotations when there are no costs and no emigration*

~ test fitness_single_locus() from run_rot() and add to Rmd
